\begin{declaration}
\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
This thesis is presented as a collection of linked chapters, already published as journal articles and conference papers, to inform the theory and practice of selecting cloud Infrastructure Service. 
Five are published as articles in peer reviewed journals, and four in peer-reviewed conferences. One paper is under review.
Some of these result from collaborative work with other researchers, I have included statements clearly outlining the extent of collaboration, with whom and under what auspices. 

\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

I therefore declare that this thesis, of which the published journal articles and book
chapters are the key part, is my own original work, except where referenced and stated
otherwise.
\end{declaration}

\clearpage